Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-04-04 paperICSME.tex
Cambiando los datos

%Conference
\conferenceinfo{MSR '16}{May 14-15, 2016, Austin, Texas, USA}

@@

%
% --- Author Metadata here ---
\conferenceinfo{MSR}{'16 Austin, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

@@

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Gema Rodr\'iguez-P\'erez\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{gerope@libresoft.es}
% 2nd. author
\alignauthor
Jesus M. Gonzalez-Barahona\\
      \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{jgb@gsyc.es}
% 3rd. author
\alignauthor Gregorio Robles\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{grex@gsyc.urjc.es}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{29 January 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

RQ2 is the main question that we want to answer in this paper: given bugs that have been fixed by changing some code, how many of those were introduced by the previous commit.
    %\item RQ1 : How can tickets which are bug reports be differentiated from those that are not?
    %\item RQ1:  How can we know that a change was done to fix a bug in the source code? How can we identify them?

@@

    \item Each time that the title or the description of a ticket describes an unexpected behavior in the program, our criteria indicated that it was considered as a bug report. 
    \item The description of the ticket presents an optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
    \item When the ticket described that some updates were required, the ticket is a bug report. We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected. 
    \item When only test files are affected in a ticket, we classified it as not being a bug report. We consider bug errors in test files are a different type of bugs, as the software may still work as expected.

@@

In this stage we have analyzed the 189 tickets\footnote{20 tickets have not been analyzed due to time constraints.} of the classified as \textit{Bug Reports}, the possible outcome of the analysis was one of the following three options:

@@

We have identified a total of 348 previous commits which could be the cause of the 189 bug reports under analysis. Then, we analyzed the bug reports together with their previous commits discarding the cases where the previous commit was a false positive (\emph{noise}) such as blank lines, changes in comments or even a change in the version of the file. So, in total we have analyzed 308 previous commits.

As can be seen in Table~\ref{tab:responsability}, from the 308 previous commits, 152 have been considered to be the cause of the bug, whereas 114 have been identified as not being the cause.

We have been unable to decide in 42 cases. Figure~8 %\ref{fig:added}
 provides an example of such a situation; the file content after the bug fix can be seen on the left in subfigure (1) and the file before the fix commit on the right in subfigure (2); as it can be observed, the only difference is lines that have been added. Figure~9 %\ref{fig:unknow}
 offers an example of a different situation, where the researchers have not been able to classify the bug due to not having sufficient knowledge of the change, the context and the project. In both cases, we have not been able to know which previous commit could be the cause of the bug, so we classified them as \textit{Undecided}.

@@

\begin{table}[htb]
\begin{center}
\begin{tabular}{lrr}
\toprule[0.3mm]
  & \multicolumn{1}{c}{Before} & \multicolumn{1}{c}{After} \\
  & \multicolumn{1}{c}{Deleting Noise} & \multicolumn{1}{c}{Deleting Noise} \\\hline
{Cause} & (152) 44\% & (152) 49\% \\[0ex]
{Not Cause} & (154) 44\% & (114) 37\% \\[0ex]
{Undecided} & (42) 12\% & (42) 14\% \\[0ex]
\bottomrule[0.3mm]
\end{tabular}
\caption{Number of times (and percentage) where the previous commit is the cause, not the cause or could not be classified, before and after deleting noise.}
\label{tab:responsability}
\end{center}
\end{table}

If we attend to how many previous commits each of the 189 bug reports analyzed had, we see that 131 only had a previous commit as in Figure~\ref{fig:3}, whereas 58 had more than one previous commit as the one in Figure~\ref{fig:manyprevious}. In Table~\ref{tab:secondStage}, from the 131 unique previous commits, 65 were the cause of the bug, while 30 did not cause the failure. For the 58 bugs that had more than one previous commit, a total number of 179 previous commits were identified; of them 86 were the cause of the bug, while 82 were not. 
%\grex{No me queda claro que quieres decir con mas de un identificador previo}\gema{supongo que despues de ver el ejemplo se entienda mejor, identificador previo se refiere a que  al arreglar el error se shan tocado varias lineas que han sido anadidas o modificadas en commit diferentes, por tanto tenemos mas de un commit diferente, aqui use identificador en vez de commit y puede ser un error}

@@

We also studied the distribution of the number of previous commits for each bug. This result will provide further insight into the bug-seeding nature; it offers as well an idea of the complexity of identifying the cause of a bug, as the more commits involved, the harder it is to identify the cause and understand it. As shown in Table~\ref{tab:secondStage2}, usually the number of commits that can be considered as previous is 1 (over 69\% of the cases), followed by 2 commits (13\%). In around 10\% of the cases, 3 or more commits are involved.

@@

\begin{table*}[htb]
\begin{center} {\footnotesize
\begin{tabular}{lccccc}
\toprule[0.3mm]
  & \multicolumn{1}{c}{One previous} & \multicolumn{1}{c}{two previous} & \multicolumn{1}{c}{three previous} & \multicolumn{1}{c}{four previous} & \multicolumn{1}{c}{+five previous}\\
  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commits} & \multicolumn{1}{c}{commits}& \multicolumn{1}{c}{commits}& \multicolumn{1}{c}{commits}\\\hline
\raisebox{1ex}{Neutron} & 11 & 3 & 2 & 2 & 0 \\[0ex]
\raisebox{1ex}{Horizon} & 39 & 8 & 3 & 2 & 4 \\[0ex]
\raisebox{1ex}{Nova} & 44 & 5 & 2 & 4 & 4 \\[0ex]
\raisebox{1ex}{Cinder} & 37 & 9 & 6 & 2 & 2\\[0ex]
\raisebox{1ex}{Total} & 131 & 25 & 13 & 10 & 10\\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\caption{ Distribution of the number of commits that can be considered as the previous commit per bug report for each project.}
\label{tab:secondStage2}
\end{center}
\end{table*}

@@

Results are given in Table~\ref{tab:secondStage3}; in 8 bug reports all the previous commits were identified as the cause, in 30 bug reports at least one of the previous commits caused the bug, and in 11 bug reports none of the previous commits introduced the bug. If we look at bugs that had two previous commits, in 4 cases both commits were the cause, in 9 cases only one of them was the cause and in another 4 cases non of them could be determined as the cause.

@@

\begin{table*}[htb]
\begin{center} {\footnotesize
\begin{tabular}{lccccc}
\toprule[0.3mm]
   & \multicolumn{1}{c}{two previous} & \multicolumn{1}{c}{three previous} & \multicolumn{1}{c}{four previous} & \multicolumn{1}{c}{+five previous} & \multicolumn{1}{c}{Total}\\
  & \multicolumn{1}{c}{commits} & \multicolumn{1}{c}{commits}& \multicolumn{1}{c}{commits}& \multicolumn{1}{c}{commits}\\\hline
\raisebox{1ex}{All are the cause}          & 4 & 3 & 0 & 1 & 8\\[0ex]
\raisebox{1ex}{At least one is the cause} & 9 & 7 & 5 & 9 & 30\\[0ex]
\raisebox{1ex}{None is the cause}         & 4 & 2 & 4 & 1 & 11\\[0ex]
\raisebox{1ex}{Undecided}                & 1 & 0 & 1 & 0 & 2\\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\caption{Number of previous commits identified as the cause of a bug per bug report}
\label{tab:secondStage3}
\end{center}
\end{table*}

@@

As any other empirical study, this one presents several threats to its validity, external and internal, that have to be considered and taken into account. In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package\footnote{\url{http://gemarodri.github.io/2016-msr-prevcommit/}} including data sources, intermediate data and scripts that can be obtained.

@@

The empirical experiment carried out in OpenStack supported that the current premise assumed does not hold for a large fraction of the analyzed bugs, because around the 40\% of the previous commits were not the cause of the bug.

>>>>

%Conference
\conferenceinfo{ICSME '16}{Oct 02-10, 2016, Raleigh, North Carolina USA}

@@

%
% --- Author Metadata here ---
\conferenceinfo{ICSME}{'16 Raleigh, North Carolina USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

@@

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Gema Rodr\'iguez-P\'erez\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{gerope@libresoft.es}
% 2nd. author
\alignauthor
Jesus M. Gonzalez-Barahona\\
      \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{jgb@gsyc.es}
% 3rd. author
\alignauthor Gregorio Robles\\
       \affaddr{GSyC/LibreSoft \\ Universidad Rey Juan Carlos}\\
       %\affaddr{1932 Wallamaloo Lane}\\
       \affaddr{Madrid, Spain}\\
       \email{grex@gsyc.urjc.es}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
\date{8 April 2016}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

RQ2 is the main question that we want to answer in this paper: given bugs that have been fixed by changing some code, how many of those were introduced by the previous commit.

@@

    \item Each time that the title or the description of a ticket describes an unexpected behaviour in the program, our criteria indicated that it was considered as a bug report. 
    \item The description of the ticket presents an optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
    \item When the ticket described that some updates were required, the ticket is a bug report. We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected. 
    \item When only test files are affected in a ticket, we classified it as not being a bug report. We consider bug errors in test files are a different type of bugs, as the software may still work as expected.

@@

In this stage we have analyzed the 209 tickets, the possible outcome of the analysis was one of the following three options:

@@

We have identified a total of 462 previous commits which could be the cause of the 209 bug reports under analysis. Then, we analyzed the bug reports together with their previous commits discarding the cases where the previous commit was a false positive (\emph{noise}) such as blank lines, changes in comments, commits added previously date of bug report or even a change in the version of the file. So, in total we have analyzed 349 previous commits.

As can be seen in Table~\ref{tab:responsability}, from the 349 previous commits, 179 have been considered to be the cause of the bug, whereas 129 have been identified as not being the cause.

We have been unable to decide in 39 cases. Figure~8 %\ref{fig:added}
 provides an example of such a situation; the file content after the bug fix can be seen on the left in subfigure (1) and the file before the fix commit on the right in subfigure (2); as it can be observed, the only difference is lines that have been added. Figure~9 %\ref{fig:unknow}
 offers an example of a different situation, where the researchers have not been able to classify the bug due to not having sufficient knowledge of the change, the context and the project. In both cases, we have not been able to know which previous commit could be the cause of the bug, so we classified them as \textit{Undecided}.

@@

\begin{table}[htb]
\begin{center}
\begin{tabular}{lrr}
\toprule[0.3mm]
 & After Deleting Noise \\\hline
{Cause}  & (179) 51\% \\[0ex]
{Not Cause} & (129) 37\% \\[0ex]
{Undecided} & (41) 12\% \\[0ex]
\bottomrule[0.3mm]
\end{tabular}
\caption{Number of times (and percentage) where the previous commit is the cause, not the cause or could not be classified, after deleting noise.}
\label{tab:responsability}
\end{center}
\end{table}

%\begin{table}[htb]
%\begin{center}
%\begin{tabular}{lrr}
%\toprule[0.3mm]
%  & \multicolumn{1}{c}{Before} & \multicolumn{1}{c}{After} \\
%  & \multicolumn{1}{c}{Deleting Noise} & \multicolumn{1}{c}{Deleting Noise} \\\hline
%{Cause} & (152) 44\% & (152) 49\% \\[0ex]
%{Not Cause} & (154) 44\% & (114) 37\% \\[0ex]
%{Undecided} & (42) 12\% & (42) 14\% \\[0ex]
%\bottomrule[0.3mm]
%\end{tabular}
%\caption{Number of times (and percentage) where the previous commit is the cause, not the cause or could not be classified, before and after deleting noise.}
%\label{tab:responsability}
%\end{center}
%\end{table}3

If we attend to how many previous commits each of the 209 bug reports analyzed had, we see that 146 only had a previous commit as in Figure~\ref{fig:3}, whereas 63 had more than one previous commit as the one in Figure~\ref{fig:manyprevious}. In Table~\ref{tab:secondStage}, from the 146 unique previous commits, 77 were the cause of the bug, while 30 did not cause the failure and 39 we didn't know the cause. For the 63 bug reports that had more than one previous commit, a total number of 203 previous commits were identified; of them 102 were the cause of the bug, while 99 were not and 2 we were unable to decide. 
%\grex{No me queda claro que quieres decir con mas de un identificador previo}\gema{supongo que despues de ver el ejemplo se entienda mejor, identificador previo se refiere a que  al arreglar el error se shan tocado varias lineas que han sido anadidas o modificadas en commit diferentes, por tanto tenemos mas de un commit diferente, aqui use identificador en vez de commit y puede ser un error}

@@

We also studied the distribution of the number of previous commits for each bug. This result will provide further insight into the bug-seeding nature; it offers as well an idea of the complexity of identifying the cause of a bug, as the more commits involved, the harder it is to identify the cause and understand it. As shown in Table~\ref{tab:secondStage2}, usually the number of commits that can be considered as previous is 1 (over 69\% of the cases), followed by 2 commits (13\%). In around 17\% of the cases, 3 or more commits are involved.

@@

\begin{table*}[htb]
\begin{center} {\footnotesize
\begin{tabular}{lccccc}
\toprule[0.3mm]
  & \multicolumn{1}{c}{One previous} & \multicolumn{1}{c}{two previous} & \multicolumn{1}{c}{three previous} & \multicolumn{1}{c}{four previous} & \multicolumn{1}{c}{+five previous}\\
  & \multicolumn{1}{c}{commit} & \multicolumn{1}{c}{commits} & \multicolumn{1}{c}{commits}& \multicolumn{1}{c}{commits}& \multicolumn{1}{c}{commits}\\\hline
\raisebox{1ex}{Neutron} & 13  & 5 & 2 & 0 & 1 \\[0ex]
\raisebox{1ex}{Horizon} & 38  & 9 & 3 & 0 & 4 \\[0ex]
\raisebox{1ex}{Nova}    & 48  & 8 & 2 & 4 & 5 \\[0ex]
\raisebox{1ex}{Cinder}  & 47  & 6 & 8 & 3 & 3\\[0ex]
\raisebox{1ex}{Total}   & 146 & 28 & 15 & 7 & 13\\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\caption{ Distribution of the number of commits that can be considered as the previous commit per bug report for each project.}
\label{tab:secondStage2}
\end{center}
\end{table*}

@@

Results are given in Table~\ref{tab:secondStage3}; in 16 bug reports all the previous commits were identified as the cause, in 33 bug reports at least one of the previous commits caused the bug, and in 12 bug reports none of the previous commits introduced the bug. If we look at bugs that had two previous commits, in 9 cases both commits were the cause, in 13 cases only one of them was the cause and in another 5 cases non of them could be determined as the cause.

@@

\begin{table*}[htb]
\begin{center} {\footnotesize
\begin{tabular}{lccccc}
\toprule[0.3mm]
   & \multicolumn{1}{c}{two previous} & \multicolumn{1}{c}{three previous} & \multicolumn{1}{c}{four previous} & \multicolumn{1}{c}{+four previous} & \multicolumn{1}{c}{Total}\\
  & \multicolumn{1}{c}{commits} & \multicolumn{1}{c}{commits}& \multicolumn{1}{c}{commits}& \multicolumn{1}{c}{commits}\\\hline
\raisebox{1ex}{One are the cause}        & 13& 1 & 1 & 4 & 19\\[0ex]
\raisebox{1ex}{Two are the cause}        & 9 & 7 & 3 & 1 & 20\\[0ex]
\raisebox{1ex}{Three are the cause}      & - & 4 & 0 & 2 & 6\\[0ex]
\raisebox{1ex}{Four are the cause}       & - & - & 0 & 1 & 1\\[0ex]
\raisebox{1ex}{+Four are the cause}      & - & - & - & 3 & 3\\[0ex]
\raisebox{1ex}{None is the cause}        & 5 & 3 & 3 & 1 & 12\\[0ex]
\raisebox{1ex}{Undecided}                & 1 & 0 & 1 & 0 & 2\\[0ex]
\bottomrule[0.3mm]
\end{tabular} }
\caption{Number of previous commits identified as the cause of a bug per bug report}
\label{tab:secondStage3}
\end{center}
\end{table*}

@@

As any other empirical study, this one presents several threats to its validity, external and internal, that have to be considered and taken into account. In order to allow others to study it in detail, replicate it or even build on top of it, we have set up a replication package\footnote{\url{http://gemarodri.github.io/2016-ICSME-prevcommit/}} including data sources, intermediate data and scripts that can be obtained.

@@

The empirical experiment carried out in OpenStack supported that the current premise assumed does not hold for a large fraction of the analyzed bugs, because around the 37\% of the previous commits were not the cause of the bug.
